---
title: "formation-quarto"
authors: "Mathieu Depetris, Clara Lerebourg, Julien Lebranchu"
toc: true
number-sections: true
format: 
  # pdf:
  #   code-line-numbers : true
  html :
    code-fold: true
prefer-html: true
editor: visual
bibliography: references.bib
---

## Code chunks

```{r, message = FALSE, warning = FALSE}
#| label: load-packages
#| echo: false

library(ggplot2)
library(dplyr)
library(kableExtra)
```

```{r}
#| label: scatterplot
#| code-fold : true

ggplot(mpg, aes(x = hwy, y = cty, color = cyl)) +
  geom_point(alpha = 0.5, size = 2) +
  scale_color_viridis_c() +
  theme_minimal()
```

# Améliorer figure

```{r}
#| label: fig-scatterplot
#| fig-cap: "City and highway mileage for 38 popular models of cars."
#| fig-alt: "Scatterplot of city vs. highway mileage for cars, where points are colored by the number of cylinders. The plot displays a positive, linear, and strong relationship between city and highway mileage, and mileage increases as the number of cylinders decreases."
#| fig-width: 6
#| fig-height: 3.5
#| code-fold : true

ggplot(mpg, aes(x = hwy, y = cty, color = cyl)) +
  geom_point(alpha = 0.5, size = 2) +
  scale_color_viridis_c() +
  theme_minimal()
```

@fig-scatterplot shows a positive, strong, and linear relationship between the city and highway mileage of these cars.

# Plusieurs figures

```{r}
#| label: fig-mpg
#| fig-cap: "City and highway mileage for 38 popular models of cars."
#| fig-subcap:
#|   - "Color by number of cylinders"
#|   - "Color by engine displacement, in liters"
#| layout-ncol: 2

ggplot(mpg, aes(x = hwy, y = cty, color = cyl)) +
  geom_point(alpha = 0.5, size = 2) +
  scale_color_viridis_c() +
  theme_minimal()

ggplot(mpg, aes(x = hwy, y = cty, color = displ)) +
  geom_point(alpha = 0.5, size = 2) +
  scale_color_viridis_c(option = "E") +
  theme_minimal()
```

The plots in @fig-mpg show the relationship between city and highway mileage for 38 popular models of cars. In @fig-mpg-1 the points are colored by the number of cylinders while in @fig-mpg-2 the points are colored by engine displacement.

# Tableaux

```{r}
#| label: table-mpg

mpg
```

```{r}
#| label: table-mpg-2

kable(mpg) %>%
  kable_classic(c("hover",
                  "condensed"), 
                font_size = 14)
```

```{r}
#| echo: false

mean_cty <- round(mean(mpg$cty), 2)
mean_hwy <- round(mean(mpg$hwy), 2)
```

There are `r nrow(mpg)` observations in our data.

The average city mileage of the cars in our data is `r mean_cty` and the average highway mileage is `r mean_hwy`.

# Citations

Faire une citation [@aguilar2002]
